A Unification of Lower Bounds on Prediction Dimension of Consistent Convex Surrogates

### 2021-01-21 colt-21/cvx-flats.tex
Asking lots of questions in the appendi about org

\begin{definition}[\jessie{Updated definition: }Flat]\label{def:flat-general}
	A \emph{flat} $F \subseteq \P$ $\subseteq \reals^n$ is a nonempty set $F = \ker_\P(W) = \{q \in \P : \E_q W = \vec 0\}$ for some $W:\Y \to \reals^d$.
	Furthermore, we define $\codim(F) := \dim(\spn(\P) / \spn(F))$.

	%recover this later
	\btw{Jessie: Suggest delete}
	If $n$ is finite, the codimension of $F$ is given by $\codim(F)=\mathrm{rank}(W)$.
	If $n$ is infinite, consider $\codim(F) = \dim(\{p + F : p \in \P\}) \leq d$.
\end{definition}

@@

\begin{lemma}\label{lem:finite-relint-dim}
  Let flat $F\subseteq \P$ contain some $p\in\relint{\P}$.
  Then $p \in \relint{F}$ and $\Pcodim(F) = \codim(F)$.
\end{lemma}
\begin{proof}
	\jessie{TODO}
	First, to observe $p \in \relint{F}$, since $p \in \relint{\P}$, we must have some ball $B(\epsilon, p) \subseteq \P$ so that $B(\epsilon, p) \cap F \subseteq F$ and is also a ball, and thus $p \in \relint{F}$.

	Moreover, to observe $\Pcodim(F) = \codim(F)$, \jessie{TODO}
\end{proof}

@@

	Suppose $F \subseteq \gamma_r$.
	We show $F \subseteq \gamma_{r'}$.
	Let $q \in F$.
	We claim that for small enough $\epsilon$, the point $q' = p - \epsilon (q-p)$ is in $F$ as well.
	Containment in $F$ follows because both $p$ and $q$ are in $F$ and it is a flat, while containment in $\P$ follows because $p \in \relint\P$.

@@

\subsection{Reconstructing the result of~\citet[Theorem 16]{ramaswamy2016convex}}
\begin{lemma}\label{lem:feas-sub-is-a-flat}
	Suppose we have the discrete elicitable property $\gamma$ and distribution $p \in \relint{\simplex}$ with $r \in \gamma(p)$.
	If $F$ is a flat so that $p \in F \subseteq \gamma_r$, then $F - p$ is a subspace contained in $\Sc_{\gamma_r}(p)$.
	\jessie{Is this what we want to show? I feel like we want $\Sc_{\gamma_r}(p)$ is a flat containing $p$.}  
	%  \raf{I think you want $p$ in the interior of the simplex for now}
\end{lemma}
\begin{proof}
	First, observe $F-p$ is a subspace as it is a linear shift of $F$, which is a linear subspace by definition of a flat and the fact that it contains $\vec 0$ (since $F$ contains $p$, which we subtract from).
	Moreover, by Lemma~\ref{lem:finite-relint-dim}, we have $p \in \relint(F)$, so $\vec 0 \in \relint{F-p}$.

@@

	As $L'$ is calibrated with respect to $\ell'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then by Theorem~\ref{thm:cvx-flats}, we know there exists a flat $F' \subseteq$ of codimension $d$ relative to $\reals^{\Y'}$ so that $\codim(F') \leq d$.
	Moreover, as $d$ is the maximal codimension of such a flat, we show in Lemma~\ref{lem:feas-sub-is-a-flat} that $\Sc_{\gamma_r}(p)$ is one such flat, and we have $\dim(\Sc_{\gamma_r}(p)) \geq \dim(F') \geq \|p\|_0 - d- 1$.
	Lemma~\ref{lem:p-boundary-fsd} then states $\dim(\Sc_{\gamma'_r}(p)) = \dim(\Sc_{\gamma_r}(p))$, and from there we observe the result.
	%	First, for intuition, consider $p \in \relint{\simplex}$. 
	%	Theorem~\ref{thm:cvx-flats} implies that there exists a flat $F'$ of affine dimension at least $n-d-1$.
	%	Lemma~\ref{lem:feas-sub-is-a-flat} then says that $\dim(\Sc_{\gamma_r}(p)) \geq \dim(F') \geq n-d-1 \implies d \geq n - \dim(\Sc_{\gamma_r}(p)) - 1$.
	%
	%	
	%	If we can show that $L' := L|_{\Y'}$ is calibrated with respect to $\ell' := \R \times \Y' \to \reals$ with $\ell(r,y) = \ell'(r,y)$ for all $r \in \R$ and $y \in \Y'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then we observe the existence of a flat $F^*$ of codimension $d$ (in $\reals^{\Y'}$) so that $\dim(F^*) = \|p\|_0 - d - 1$ by Theorem~\ref{thm:cvx-flats}.
	%	Then we can use Lemma~\ref{lem:p-boundary-fsd} to observe $\dim(\Sc_{\gamma'_r}(p)) = \dim(\Sc_{\gamma_r}(p))$, and thus the result holds.
	%	
	%	Now to see that $L'$ is calibrated with respect to $\ell'$, consider that $\gamma(p) = \gamma'(p)$ for all $p \in \Delta^{\Y'}$,
	%	\begin{align*}
	%		\forall p \in \Delta_{\Y'}:  \inf_{u \in \reals^d : \psi(u) \not \in \gamma'(p)} L'(u;p) = \inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} L(u;p) > \inf_{u \in \reals^d} L(u;p) = \inf_{u \in \reals^d} L'(u;p)~.~
	%	\end{align*}
	%	Therefore, we have $L'$ calibrated with respect to $\ell'$.
	%
	%	Moreover, we want to show $L'$ indirectly elicits $\gamma'$ so we can apply Theorem~\ref{thm:cvx-flats}.
	%	First, observe that $L'$ elicits $\Gamma' : p \mapsto \Gamma(p)$ for all $p \in \Delta_{\Y'}$ 
	%	For all $p \in \simplex$, we have $u \in \Gamma(p) \implies \psi(u) \in \gamma(p)$.
	%	As $\Delta_{\Y'} \subseteq \simplex$, this is in particular true for all $p \in \Delta_{\Y'}$.
	%	Therefore, for all $p \in \Delta_{\Y'}$, we have $\Gamma'_u = \Gamma_u \cap \Delta_{\Y'} \subseteq \gamma_{\psi(u)} \cap \Delta_{\Y'} = \gamma'_{\psi(u)}$, and thus $L'$ indirectly elicits $\gamma'$.
\end{proof}

>>>>

\jessie{Differentiate between $\ker$ and $\zeros$}
\begin{definition}[\jessie{Updated definition: }Flat]\label{def:flat-general}
	A \emph{flat} $F \subseteq \P$ $\subseteq \reals^n$ is a nonempty set $F = \ker_\P(W) = \{q \in \P : \E_q W = \vec 0\}$ for some $W:\Y \to \reals^d$.
	Furthermore, we define $\codim(F) := \dim(\spn(\P) / \spn(F))$.

\end{definition}

@@

\begin{lemma}\label{lem:finite-relint-dim}
  Let flat $F\subseteq \P$ contain some $p\in\relint{\P}$.
  Then $p \in \relint{F}$ and \jessie{Originally $\Pcodim(F) = \codim(F)$? Also; $F$ vs $F'$?}.
\end{lemma}
\begin{proof}
	\jessie{TODO: write out def of relint (algebraic definition) to be explicit}
	Since $p \in \relint{\P}$, there is some small enough $\epsilon > 0 $ so that for $q \in \P, \alpha \in (-\epsilon,\epsilon)$, the point $q_\alpha := p - \alpha(q - p)$ is still in $\P$.
	In particular, if $q \in F$, then $q_\alpha \in F$, as it is a linear combination of elements of $F$, which is a convex set as it is a flat.
	Therefore, $p \in \relint{F}$.

		\bigskip
	\jessie{Where does this belong? Cause it's not here.}
	Now let $T_V : \spn(\P) \to \reals^d$ be the function mapping $q \mapsto \E_q V$ for the function $V$ given by Threorem~\ref{thm:convex-flats-inf-dim}.
	Let $p \in \relint{\simplex} \cap F$, and define $F' := F - \{p\}$, and similarly define $P' := P - \{p\}$ and $T'_V(v) = \E_{Y \sim v} V(Y)$.

	Now let $v \in \ker(T'_V)$ (so that $q = p + v$).
	There must exist an $\epsilon > 0$ so that $\epsilon v \in F'$ since, by Lemma~\ref{lem:finite-relint-dim}, we have $p \in \relint{\simplex}$, and therefore $\vec 0 \in \relint{F'}$.
	Moreover, we have $\epsilon v \in \ker(T'_V)$ by construction, since both $v$ and $\vec 0$ are in the kernel; this implies that $\spn(F') = \ker(T'_V)$.

	Moreover, we want to observe $F' = P' \cap \ker(T'_V)$.
	In order to see this, consider $v \in F' \iff v + p \in F$, and similarly for $\P'$ and $\ker(T'_V)$.
	Now, as $F \subseteq P$ by construction, we have $F' \subseteq P'$, and since $\spn(F') = \ker(T'_V)$, we additionally have $F' \subseteq \ker(T'_V)$, yielding $F' \subseteq P' \cap \ker(T'_V)$.
	Now consider $v \in \P' \cap \ker(T'_V)$; we know that $\E_v V = \vec 0$, and therefore, $\E_{q} = \vec 0 $, so $v \in F'$, thus showing $F' = P' \cap \ker(T'_V)$.

	Therefore, we have $\dim(\spn(F')) = \dim(\ker(T'_V)) \geq \dim(\spn(P')) - d$ by \jessie{isomorphism theorem} since $F' = \ker(T'_V) \cap P'$.
	When we substitute $P = \simplex$, this yields the bound $\dim(\spn(F')) \geq n - 1 - d$.
\end{proof}

@@

	Suppose $F \subseteq \gamma_r$.
	We show $F \subseteq \gamma_{r'}$.
	Let $q \in F$.
	%By Lemma~\ref{lem:finite-relint-dim}, we also have $p \in \relint{F}$
	We claim that for small enough $\epsilon$, the point $q' = p - \epsilon (q-p)$ is in $F$ as well.
	Containment in $F$ follows because both $p$ and $q$ are in $F$ and it is a flat, while containment in $\P$ follows because $p \in \relint\P$.

@@

\subsection{Reconstructing the result of~\citet[Theorem 16]{ramaswamy2016convex}}
\begin{lemma}\label{lem:feas-sub-is-a-flat}
	Suppose we have the discrete elicitable property $\gamma$ and distribution $p \in \relint{\simplex}$ with $r \in \gamma(p)$.
	If $F$ is a flat so that $p \in F \subseteq \gamma_r$, then $F' := F - \{p\}$ is a subspace contained in $\Sc_{\gamma_r}(p)$.
	%  \raf{I think you want $p$ in the interior of the simplex for now}
\end{lemma}
\begin{proof}
	We aim to show $v \in F' \implies v \in \Sc_{\gamma_r}(p)$.
	First, observe $v \in F' \iff p + v \in F$.
	As $p \in \relint{\simplex}$, by Lemma~\ref{lem:finite-relint-dim}, we additionally have $p \in \relint{F}$, and in turn $\vec 0 \in \relint{F'}$.\jessie{Last part irrelevant?}

	Suppose $v \in F'$, and since $p \in \relint{F}$, there is an $\epsilon > 0$ so that for all $\alpha \in (-\epsilon, \epsilon)$, we have $p + \alpha v \in F \implies p + \alpha v \in \gamma_r$, since $F$ is convex, as are level sets of elicitable properties~\cite{lambert2009eliciting}.
	By definition of $\Sc_{\gamma_r}(p)$, there is then an $\epsilon$ satisfying the requirement for $v \in \Sc_{\gamma_r}(p)$, so we can conclude $v \in \Sc_{\gamma_r}(p)$, yielding the desired result.

	\bigskip

@@

	As $L'$ is calibrated with respect to $\ell'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then by Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}, we know there exists a flat with $p \in F' \subseteq \gamma'_r$ \jessie{NOTATION- this $F'$ isn't $F - \{p\}$} of \Pcodimension at most $d$.\jessie{To my understanding, we still don't relate \Pcodimension to dimension? Or did I just miss that.}
	Moreover, as $d$ is the maximal codimension of such a flat, we show in Lemma~\ref{lem:feas-sub-is-a-flat} that $\Sc_{\gamma_r}(p)$ is one such flat, and we have $\dim(\Sc_{\gamma_r}(p)) \geq \dim(F - \{p\}) \geq \|p\|_0 - d- 1$ by Lemma~\jessie{??}.
	Lemma~\ref{lem:p-boundary-fsd} then states $\dim(\Sc_{\gamma'_r}(p)) = \dim(\Sc_{\gamma_r}(p))$, and from there we observe the result.
	%	First, for intuition, consider $p \in \relint{\simplex}$. 
	%	Theorem~\ref{thm:cvx-flats} implies that there exists a flat $F'$ of affine dimension at least $n-d-1$.
	%	Lemma~\ref{lem:feas-sub-is-a-flat} then says that $\dim(\Sc_{\gamma_r}(p)) \geq \dim(F') \geq n-d-1 \implies d \geq n - \dim(\Sc_{\gamma_r}(p)) - 1$.
	%
	%	
	%	If we can show that $L' := L|_{\Y'}$ is calibrated with respect to $\ell' := \R \times \Y' \to \reals$ with $\ell(r,y) = \ell'(r,y)$ for all $r \in \R$ and $y \in \Y'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then we observe the existence of a flat $F^*$ of codimension $d$ (in $\reals^{\Y'}$) so that $\dim(F^*) = \|p\|_0 - d - 1$ by Theorem~\ref{thm:cvx-flats}.
	%	Then we can use Lemma~\ref{lem:p-boundary-fsd} to observe $\dim(\Sc_{\gamma'_r}(p)) = \dim(\Sc_{\gamma_r}(p))$, and thus the result holds.
	%	
	%	Now to see that $L'$ is calibrated with respect to $\ell'$, consider that $\gamma(p) = \gamma'(p)$ for all $p \in \Delta^{\Y'}$,
	%	\begin{align*}
	%		\forall p \in \Delta_{\Y'}:  \inf_{u \in \reals^d : \psi(u) \not \in \gamma'(p)} L'(u;p) = \inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} L(u;p) > \inf_{u \in \reals^d} L(u;p) = \inf_{u \in \reals^d} L'(u;p)~.~
	%	\end{align*}
	%	Therefore, we have $L'$ calibrated with respect to $\ell'$.
	%
	%	Moreover, we want to show $L'$ indirectly elicits $\gamma'$ so we can apply Theorem~\ref{thm:cvx-flats}.
	%	First, observe that $L'$ elicits $\Gamma' : p \mapsto \Gamma(p)$ for all $p \in \Delta_{\Y'}$ 
	%	For all $p \in \simplex$, we have $u \in \Gamma(p) \implies \psi(u) \in \gamma(p)$.
	%	As $\Delta_{\Y'} \subseteq \simplex$, this is in particular true for all $p \in \Delta_{\Y'}$.
	%	Therefore, for all $p \in \Delta_{\Y'}$, we have $\Gamma'_u = \Gamma_u \cap \Delta_{\Y'} \subseteq \gamma_{\psi(u)} \cap \Delta_{\Y'} = \gamma'_{\psi(u)}$, and thus $L'$ indirectly elicits $\gamma'$.
\end{proof}
